%%===============================================================
%%===============================================================

\begin{thebibliography}{99}

%%=======
\bibitem{Secanell13} M. Secanell, V. Zingan, M. Bhaiya, P. Wardlaw, M. Moore, K. Domican and P. Dobson, Fuel Cell Simulation Toolbox, User's Guide, 2015. URL: http://www.openfcst.org.
%%=======
\bibitem{Secanell07} M. Secanell, Computational Modeling and Optimization of Proton Exchange Membrane Fuel Cells, Ph.D. thesis, University of Victoria, November 2007.
%%=======
\bibitem{Secanell07b} M. Secanell et al., Multi-variable optimization of PEMFC cathodes using an agglomerate model, \textit{Electrochimical Acta}, 52(7):2668-2682, 2007.
%%=======
\bibitem{Secanell08} M. Secanell, R. Songprakorp, A. Suleman, N. Djilali.  Multi-objective optimization of a polymer electrolyte fuel cell membrane electrode assembly. Energy and Environmental Science. 1:378-388, 2008.
%%=======
\bibitem{Dobson12} Dobson P., Lei C., Navessin T., Secanell M., Characterization of the PEM fuel cell catalyst layer microstructure by nonlinear least-squares parameter estimation, \textit{Journal of the Electrochemical Society}, 159:B514-B523, 2012.
%%=======
\bibitem{svnhelp13} Setting the \$Id\$ Tag in Subversion. http://www.startupcto.com/server-tech/subversion/setting-the-id-tag. Accessed on April 6, 2015.
%%=======
\bibitem{Secanell14} M. Secanell, A. Putz, P. Wardlaw, V. Zingan, M. Bhaiya, M. Moore, J. Zhou, C. Balen and K. Domican, OpenFCST: An Open-Source Mathematical Modelling Software for Polymer Electrolyte Fuel Cells, \textit{ECS Transactions}, 64(3):655-680.
%%=======
\bibitem{Moore13} M. Moore, A. Putz and M. Secanell, Investigation of the ORR Using the Double-Trap Intrinsic Kinetic Model, Journal of the Electrochemical Society 160(6): F670-F681, 2013.
%%=======
\bibitem{Sabharwal2016analysis} M. Sabharwal, L.M. Pant, A. Putz, D. Susac, J. Jankovic, M. Secanell, Analysis of Catalyst Layer Microstructures: From Imaging to Performance, Fuel Cells, 2016.


\end{thebibliography}


%%===============================================================
%%===============================================================